### 2014-03-26 paper/exampleobjects.tex
start of video draft, figure images, pen holder files

\valkyrie{Bj\"{o}rn, I can't figure out what happened to my figures?  and why they got thrown down into a weird state with my limitations section, which appears now in two places???}

@@

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/placeholder/brain.jpg}
\caption{A touch-sensitive brain whose tubes are filled with conductive paint.  Sensing is done on a single wire via SFCS.  Inset shows the internal structure of the tubes generated by our design tool.}\input{limitations.tex}

\label{fig:toys}
\end{figure}

@@

Our presence-aware pen holder can distinguish which tool or tools a user has picked up (see Figure \ref{fig:pens}).  Our pen holder uses a modification of the FlyEye technique described by Wimmer in \cite{Wimmer-flyeye} and contains open tubes filled with fiber optic cables, one per pen chamber.  We use a single cable per chamber; our 6mm diameter fiber optic cables, in comparison to the angel hair tubes used in the original work, can send and receive through the same cable.  At the base of each tube is a QRE1113 line sensor digital breakout board, which has an integrated IR emitter and receiver.   When a pen is in its appointed place, the emitted infrared light is reflected off its bottom and travels back to the receiver, where it registers as bright.  This prototype was built by our Objet and support was flushed post-print. \valkyrie{this whole paragraph is unclear}

@@

We created a maze game with a single particle trapped in a fully enclosed tube.  To fabricate the tube, we created it in two halves that were fastened together via glue, due to limitations in our ability to remove support material otherwise.  We created this prototype on our Makerbot in two halves to allow for insertion of the marble.

>>>>

@@

\begin{figure}[h]
\centering
    \includegraphics[width=3.4in]{figures/placeholder/brain.jpg}
\caption{A touch-sensitive brain whose tubes are filled with conductive paint.  Sensing is done on a single wire via SFCS.  Inset shows the internal structure of the tubes generated by our design tool.}
\label{fig:toys}
\end{figure}

@@

Our presence-aware pen holder can distinguish which tool or tools a user has picked up (see Figure \ref{fig:pens}).  Our pen holder uses a modification of the FlyEye technique described by Wimmer in \cite{Wimmer-flyeye} and contains open tubes filled with fiber optic cables, one per pen chamber.  We use a single cable per chamber; our 6mm diameter fiber optic cables, in comparison to the angel hair tubes used in the original work \bjoern{Mixed terminology between el wire and fiber optics? "angel hair" is a specific product name, not a general technical term (I think)}, can send and receive through the same cable.  At the base of each tube is a QRE1113 line sensor digital breakout board, which has an integrated IR emitter and receiver.   When a pen is in its appointed place, the emitted infrared light is reflected off its bottom and travels back to the receiver, where it registers as bright.  This prototype was built by our Objet and support was flushed post-print. \valkyrie{this whole paragraph is unclear}

@@

We created a maze game with a single particle trapped in a fully enclosed tube.  To fabricate the tube, we created it in two halves that were fastened together via glue, due to limitations in our ability to remove support material otherwise.  We created this prototype on our Makerbot in two halves to allow for insertion of the marble. \bjoern{You are giving two different reasons here for printing in pieces.}

### 2014-03-26 paper/tubes.tex

To allow makers to design novel objects with pipe-powered interfaces, we created a tool for use on arbitrary 3D models.  This tool allows designers to select exterior connection points of their pipes (see Figure \ref{fig:tool-process-interior}) or to import vector art describing the pipes' interior paths (see Figure \ref{fig:tool-process-exterior}).  Once the maker's selections are made, we create a complete routing using either the exterior connection point method (A*, physical simulation) or the interior path method (graph edge creation, Euler circuit generation).  We thicken our routing to create pipes. \valkyrie{We also apply templates where appropriate (e.g., 3D cross-overs for tubes that intersect in the plane).}  The resultant pipes are subtracted from the original mesh, which can then be 3D printed.

Our tool is implemented as a part of Meshmixer, a consumer 3D mesh editing tool, in C++.

@@

To create pipes in which the location and shape of exterior connection points matters, we first allow makers to select the connection points on the mesh's surface using a brush. Our tool then creates an initial shortest-path routing using A* to estimate the routed distance between points.  This routing is used to create a rod; we run physics-based simulation steps on the rod to minimize its bending energy (and thereby minimize the bend radius of the tubes).

\begin{figure}[h!]
\centering
    \includegraphics[width=3.4in]{figures/placeholder/exterior.jpg}
\caption{An example mesh with exterior connection points selected.  The initial A* routing is drawn in {\color{red}red}, and in {\color{tovi}green} is our physically-based rod after simulation.}
\label{fig:tool-process-exterior}
\end{figure}

@@

Our basic first-pass routing algorithm uses the A* routing algorithm \cite{Hart-Astar}.  The path cost in our implementation is based only on shortest distance between the starting and ending points, without weighting for distance from the surface.  We only permit the routing within the voxel grid of the mesh: i.e., the routing is not permitted to traverse through space outside the mesh itself.

Given this initial routing, we create a rod of slightly longer proportional length.  The rod must be longer, as the A* routing can follow the mesh boundaries and the rod requires extra length to be pushed away from the mesh surface.  While we do not have a theoretical basis for this proportional increase, \valkyrie{yet.  what might it be related to?  we can test how much of the A* path is outside the model, and how much is inside; further we can consider the distance from the A* path that is outside the model to the surface.  I think there's a good way to do this.  It might even just mean iteratively changing the rod length until we get something reasonably short and also smooth.  we can also return to the A* that I wrote which finds a routing through the mesh that respects its boundaries; this would get us closer to what we need for length in the first place.}, we have found 1.15 to be a reasonable multiplier in practice.  A too-long rod is forced to kink and expand further than necessary inside the model, while a too-short rod must be stretched, leading to non-smooth bending.

To allow for easiest insertion of media post-print, our physical simulation step minimizes the bend radius of the generated rods.  In order to force our simulated rods away from the surface of the mesh, we create ``wind'' pushing inward from the exterior of the mesh.  This wind keeps the resulting pipe away from the surface. \valkyrie{Ryan: How does it actually work?}

@@

\subsubsection{Pipes with Non-Round Endpoints}
Our tool does not explicitly allow makers to design the shape of their pipes' endpoints.  However, the larger Meshmixer package does allow brushing arbitrary shapes onto the surface and extruding them inward, as in Figure \ref{fig:meshmixer-endpoint}.

@@

@@

\begin{figure}[h!]
\centering
    \includegraphics[width=3.4in]{figures/interior.pdf}
\caption{An input vector graphics file with the points which cannot be tubed as drawn highlighted in {\color{blue}blue} (a).  The connected graph created by our software (b) and the resulting Euler circuit (c) permit creation of a novel neon sign (d).}
\label{fig:tool-process-interior}
\end{figure}

\subsubsection{Routing}
The interior path routing problem is a version of the Chinese Postman Problem\footnote{The CPP is also known as the route inspection problem: \url{http://en.wikipedia.org/wiki/Route_inspection_problem}}, in which we wish to traverse all edges of the graph described in the user's input with a single Euler circuit, much as a postman needs to walk along every road at least once to deliver mail.  We call our relaxation the Spiderman Postman Problem: we allow the creation of non-existing paths (i.e., the postman may traverse buildings in addition to roads).  If inputted path components are disconnected, we must create edges that connect them; additionally we can create new edges connecting odd-degree vertices rather than simply retracing existing edges.  In the final artifact, all created edges will be blocked out by dark material so the inserted medium is not visible (see Figure \ref{fig:tool-process-interior}).  We offer a short algorithm here, with a more mathematically precise definition and associated proof in the appendix.

@@

In order to connect disconnected subgraphs in the input, we reduce each disconnected subgraph to a point.  We add edges from each subgraph-point to each other subgraph-point that represent the minimum distance between any two points in the expanded subgraphs (where distance is Euclidean distance).  We greedily select the smallest weight edges until all subgraphs are joined into a single graph.  We re-expand the subgraphs.

@@

Once we have a semi-Eulerian graph, we need to create an Euler tour.  An Euler tour is a path that touches every edge once, beginning and ending at the two nodes of odd degree: in this case, those are the user-selected start and end nodes.  We use a weighted modification of Fleury's algorithm\footnote{\url{http://en.wikipedia.org/wiki/Eulerian_path\#Fleury.27s_algorithm}} for this, where instead of randomly selecting from non-bridge paths at each node, we select the path which turns the least from the most recent path (i.e., we prefer to pass straight through a node, if possible).  This minimizes turns in the final artifact, which eases support material removal and assembly.

@@

>>>>

\bjoern{Lead with the general goals of tools to help users leverage pipes. E.g. List design goals or requirements. Them describe our tool and how it satisfies these requirements.}
To allow makers to design novel objects with pipe-powered interfaces, we created a tool for use on arbitrary 3D models.  This tool allows designers to select exterior connection points of their pipes (see Figure \ref{fig:tool-process-interior}) or to import vector art describing the pipes' interior paths (see Figure \ref{fig:tool-process-exterior}).  Once the maker's selections are made, we create a complete routing using either the exterior connection point method (A*, physical simulation) or the interior path method (graph edge creation, Euler circuit generation).  We thicken our routing to create pipes. \valkyrie{We also apply templates where appropriate (e.g., 3D cross-overs for tubes that intersect in the plane).}  The resultant pipes are subtracted from the original mesh, which can then be 3D printed.

Our tool is implemented as a part of Meshmixer, a consumer 3D mesh editing tool, in C++.  \bjoern{add a reference to meshmixer}

@@

To create pipes in which the location and shape of exterior connection points matters, we first allow makers to select the connection points on the mesh's surface using a brush  \bjoern{Need to add detail that you voxelize the mesh and route on the voxel grid. Add justification why this is a good way to do this and why a* is the right algorithm. (I guess this is oping in the next paragraph)}. Our tool then creates an initial shortest-path routing using A* to estimate the routed distance between points.  This routing is used to create a rod; we run physics-based simulation steps on the rod to minimize its bending energy (and thereby minimize the bend radius of the tubes).

\begin{figure}[h!]
\centering
    \includegraphics[width=3.4in]{figures/placeholder/exterior.jpg}
\caption{An example mesh with exterior connection points selected.  The initial A* routing is drawn in {\color{red}red}, and in {\color{tovi}green} is our physically-based rod after simulation. \bjoern{Tis example is strange. Why wouldn't be a good idea to route through the air outside the model during A*? How is A* in this case more useful than just drawing a straight line form start to end, regardless of the model geometry?}}
\label{fig:tool-process-exterior}
\end{figure}

@@

\bjoern{Need to say something in this section about avoiding intersection with previously routed pipes - how does that work? Is it because pipe interiors are now "outside"? Say this explicitly.

Also, mention somewhere that we don't yet solve the general routing problem with many routes - we only make greedy pair wise decisions.}
Our basic first-pass routing algorithm uses the A* routing algorithm \cite{Hart-Astar}.  The path cost in our implementation is based only on shortest distance between the starting and ending points, without weighting for distance from the surface.  We only permit the routing within the voxel grid of the mesh: i.e., the routing is not permitted to traverse through space outside the mesh itself.

Given this initial routing, we create a rod of slightly longer proportional length.  The rod must be longer, as the A* routing can follow the mesh boundaries and the rod requires extra length to be pushed away from the mesh surface.  While we do not have a theoretical basis for this proportional increase, \valkyrie{yet.  what might it be related to?  we can test how much of the A* path is outside the model, and how much is inside; further we can consider the distance from the A* path that is outside the model to the surface.  I think there's a good way to do this.  It might even just mean iteratively changing the rod length until we get something reasonably short and also smooth.  we can also return to the A* that I wrote which finds a routing through the mesh that respects its boundaries; this would get us closer to what we need for length in the first place.}, we have found 1.15 to be a reasonable multiplier in practice.  A too-long rod is forced to kink and expand further than necessary inside the model, while a too-short rod must be stretched, leading to non-smooth bending.  \bjoern{Once you start describing ad hoc changes, I start to wonder if there are alternative approaches to this routing problem that would feel more principled. This suggests we need a stronger argument for rod bending.}

To allow for easiest insertion of media post-print, our physical simulation step minimizes the bend radius of the generated rods.  In order to force our simulated rods away from the surface of the mesh, we create ``wind'' pushing inward from the exterior of the mesh.  This wind keeps the resulting pipe away from the surface. \valkyrie{Ryan: How does it actually work?}  \bjoern{Unrelated? Note from our call today: argue somewhere in the paper that the geometries we create would be very tricky to impossible to create with other manufacturing technologies like injection molding.}

@@

\subsubsection{Pipes with Non-Round Endpoints}
Our tool does not explicitly allow makers to design the shape of their pipes' endpoints.  However, the larger Meshmixer package does allow brushing arbitrary shapes onto the surface and extruding them inward, as in Figure \ref{fig:meshmixer-endpoint}. \bjoern{Need to motivate the "inward" phrase here? I assume  to helps with brushing on of conductive paint, but do you need this extrusion in general?}

@@

\bjoern{A general point - even though we focus on uses that require manual post print assembly, we may want to think about how useful our software is once fancier printers do come along that can do more. I think some of the contributions will still hold, which would be great.}

\bjoern{Do we have a second use case for paths beyond neon signs? Would be nice.}

@@

\begin{figure}[h!]
\centering
    \includegraphics[width=3.4in]{figures/interior.pdf}
\caption{An input vector graphics file with the points which cannot be tubed as drawn highlighted in {\color{blue}blue} (a).  The connected graph created by our software (b) and the resulting Euler circuit (c) permit creation of a novel neon sign (d). \bjoern{Shouldnt the right arrow on the top of the t point in the other direction?}}
\label{fig:tool-process-interior}
\end{figure}

\subsubsection{Routing}
\bjoern{You may want to include a primer on graphs and Euler tours here to remind the reader...}
The interior path routing problem is a version of the Chinese Postman Problem\footnote{The CPP is also known as the route inspection problem: \url{http://en.wikipedia.org/wiki/Route_inspection_problem}}, in which we wish to traverse all edges of the graph described in the user's input with a single Euler circuit, much as a postman needs to walk along every road at least once to deliver mail.  We call our relaxation the Spiderman Postman Problem: we allow the creation of non-existing paths (i.e., the postman may traverse buildings in addition to roads).  If input path components are disconnected, we must create edges that connect them; additionally we can create new edges connecting odd-degree vertices rather than simply retracing existing edges.  In the final artifact, all created edges will be blocked out by dark material so the inserted medium is not visible (see Figure \ref{fig:tool-process-interior}).  We offer a short algorithm here, with a more mathematically precise definition and associated proof in the appendix.

@@

In order to connect disconnected subgraphs in the input, we reduce each disconnected subgraph to a point \bjoern{Hw do you pick that point? Don't you reduce it to two points for inbound and outbound connections? I guess I don't follow this paragraph.}.  We add edges from each subgraph-point to each other subgraph-point that represent the minimum distance between any two points in the expanded subgraphs (where distance is Euclidean distance).  We greedily select the smallest weight edges until all subgraphs are joined into a single graph.  We re-expand the subgraphs.

@@

Once we have a semi-Eulerian graph, we need to create an Euler tour  \bjoern{Good explanation of terminology here, but you probably need this earlier.}.  An Euler tour is a path that touches every edge once, beginning and ending at the two nodes of odd degree: in this case, those are the user-selected start and end nodes.  We use a weighted modification of Fleury's algorithm for finding Euler tours\footnote{\url{http://en.wikipedia.org/wiki/Eulerian_path\#Fleury.27s_algorithm}} for this,  \bjoern{This may bee too low level a detail if you don't explain how fleury works at a conceptual level. }where instead of randomly selecting from non-bridge paths at each node, we select the path which turns the least from the most recent path (i.e., we prefer to pass straight through a node, if possible).  This minimizes turns in the final artifact, which eases support material removal and assembly.

@@

\bjoern{Too specific. This section is not just about el wire.

A most, say, this is required in the general case, but not for the specific applications we have tested so far, so we leave it to future work.

Of course it'd be great to get it to run.}
